An indexed construction of semi-cubical types

### 2021-07-09 paper/paper.tex
[paper] One figure left to clean up
[Cubical] Blow away first branch of cohbox with exfalso
The other branch looks manageable now. Lots of args specified
explicitly, to get rid of the annoying funs appearing everywhere.

\begin{figure*}
  \centerline{ \framebox{$
        \begin{array}{llcl}
          \cohbox{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}}   & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}{n,p}(D))\end{array}  & :      & \!\!\!\begin{array}{ll}\downbox{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))\end{array}                                                                              \\
          \cohbox{l,\epsilon,\epsilon',q,r}{n,0}                               & D~\unitpoint                     & \defeq & \reflett(\unitpoint)                                                                                         \\
          \cohbox{l,\epsilon,\epsilon',q,r}{n,p'+1}                            & D~(d,b)                          & \defeq & (\cohbox{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d),\cohlayer{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d)(b))           \\
          \\
          \cohlayer{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p < r \leq q \leq n - 2]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}{n,p}(D))\\(b:\mylayer{l}{n,p}(D)(d))\end{array}  & :      & \!\!\!\begin{array}{ll}\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downlayer{l,\epsilon',r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))\end{array}                                                                              \\
          \cohlayer{l,\epsilon,\epsilon',q,r}{n,p}                             & D~d~c                            & \defeq & \!\!\begin{array}{l}(\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L),\\\;\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R))\end{array}                                                                               \\
          \\
          \cohcube{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}{n,p}(D))\\(b:\mycube{l}{n,p}(D)(E)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downcube{l,\epsilon',r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\epsilon',r}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downcube{l,\epsilon,q+1}{n,p}(D)(E)(d)(b))\end{array}                                                                             \\
          \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p=r]}                        & D~E~d~(b,\_)                     & \defeq & \reflett(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',p}{n,p}(D)(d))(b_{\epsilon})) \\
          \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p<r]}                        & D~E~d~(b,c)                      & \defeq & \!\!\begin{array}{l}(\cohlayer{l,\epsilon,\epsilon',q,r}{n,p}(D)(d)(b),\;\cohcube{l,\epsilon,\epsilon',q,r}{n,p+1}(D)(E)(d,b)(c))\end{array}                                                                               \\
        \end{array}
      $}}
  \caption{Definition of a homogeneous bare cubical set (commutation of $q$-th projection and $r$-th projection)}
  \label{fig:barecubicalsetcoherences}
\end{figure*}

@@

\begin{figure*}
  \centerline{ \framebox{$
        \begin{array}{llcl}
          \multicolumn{4}{c}{\mbox{$q$-th projection of an $n$-box}}                                                                                                                            \\
          \\
          \fulldownbox{l,\epsilon,q}{n,[q < n]}   & (D:\partialcubset{l}{n})~(d:\myfullbox{l}{n}(D))     & :      & \myfullbox{l}{n-1}(\hd(D))                                                  \\
          \fulldownbox{l,\epsilon,q}{n}           & D~(d,\_)                                             & \defeq & \downbox{l,\epsilon,q}{n,n-1}(D)(d)                                         \\
          \\
          \multicolumn{4}{c}{\mbox{$q$-th face of an $n$-cube}}                                                                                                                                 \\
          \\
          \fulldowncube{l,\epsilon,q}{n,[q < n]}  & (D:\partialcubset{l}{n+1})~(c:\myfullcube{l}^{n}(D)) & :      & \myfullcube{l}^{n-1}(\hd(D))                                                \\
          \fulldowncube{l,\epsilon,q}{n}          & (D,E)~c                                              & \defeq & \downcube{l,\epsilon,q}{n,0}(D)(E)(\star)(c)                                \\
          \\
          \multicolumn{4}{c}{\mbox{\textit{where the extension of $\downbox{l}{}$ to $p>q$ is}}}                                                                                                \\
          \\
          \downbox{l,\epsilon,q}{n,p,[q < p < n]} & (D:\partialcubset{l}{n})~(d:\mybox{l}{n,p}(D))       & :      & \myfullbox{l}{n-1}(\hd(D))                                                  \\
          \downbox{l,\epsilon,q}{n,q+1}           & D~(d,b)                                              & \defeq & \border{l}^{n-1,q}(\hd(D))(\downbox{l,\epsilon,q}{n,q}(D)(d))(b_{\epsilon}) \\
          \downbox{l,\epsilon,q}{n,p,[q < p-1]}   & D~(d,b)                                              & \defeq & \downbox{l,\epsilon,q}{n,p-1}(D)(d)
        \end{array}
      $
    }}
  \caption{Standard derived notions (continued)}
  \label{fig:macroscont}
\end{figure*}

\printbibliography

>>>>

\begin{eqntable}{Definition of a homogeneous bare cubical set (commutation of $q$-th projection and $r$-th projection)}

  \eqnline{\cohbox{l,\epsilon,\epsilon',q,r}{\multicell{n,p \\ [p \leq r \leq q \leq n - 2]}}}{\multicell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\multicell{\downbox{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))}}

  \eqnline{\cohbox{l,\epsilon,\epsilon',q,r}{n,0}}{D~\unitpoint}{\defeq}{\reflett}{(\unitpoint)}

  \eqnline{\cohbox{l,\epsilon,\epsilon',q,r}{n,p'+1}}{D~(d,b)}{\defeq}{(\cohbox{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d),\cohlayer{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d)(b))}

  \cohlayer{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p < r \leq q \leq n - 2]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}{n,p}(D))\\(b:\mylayer{l}{n,p}(D)(d))\end{array}  & :      & \!\!\!\begin{array}{ll}\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downlayer{l,\epsilon',r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))\end{array}                                                                              \\
  \cohlayer{l,\epsilon,\epsilon',q,r}{n,p}                             & D~d~c                            & \defeq & \!\!\begin{array}{l}(\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L),\\\;\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R))\end{array}                                                                               \\
  \\
  \cohcube{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}{n,p}(D))\\(b:\mycube{l}{n,p}(D)(E)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downcube{l,\epsilon',r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\epsilon',r}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downcube{l,\epsilon,q+1}{n,p}(D)(E)(d)(b))\end{array}                                                                             \\
  \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p=r]}                        & D~E~d~(b,\_)                     & \defeq & \reflett(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',p}{n,p}(D)(d))(b_{\epsilon})) \\
  \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p<r]}                        & D~E~d~(b,c)                      & \defeq & \!\!\begin{array}{l}(\cohlayer{l,\epsilon,\epsilon',q,r}{n,p}(D)(d)(b),\;\cohcube{l,\epsilon,\epsilon',q,r}{n,p+1}(D)(E)(d,b)(c))\end{array}
\end{eqntable}

@@

\begin{eqntable}{Standard derived notions (continued)}
  \mc{$q$-th projection of an $n$-box}

  \eqnline{\fulldownbox{l,\epsilon,q}{n,[q < n]}}{(D:\partialcubset{l}{n})~(d:\myfullbox{l}{n}(D))}{:}{\myfullbox{l}{n-1}(\hd(D))}

  \eqnline{\fulldownbox{l,\epsilon,q}{n}}{D~(d,\_)}{\defeq}{\downbox{l,\epsilon,q}{n,n-1}(D)(d)}

  \\ \mc{$q$-th face of an $n$-cube}

  \eqnline{\fulldowncube{l,\epsilon,q}{n,[q < n]}}{(D:\partialcubset{l}{n+1})~(c:\myfullcube{l}^{n}(D))}{:}{\myfullcube{l}^{n-1}(\hd(D))}

  \eqnline{\fulldowncube{l,\epsilon,q}{n}}{(D,E)~c}{\defeq}{\downcube{l,\epsilon,q}{n,0}(D)(E)(\star)(c)}

  \\ \mc{where the extension of \downbox{l} to $p>q$ is}

  \eqnline{\downbox{l,\epsilon,q}{n,p,[q < p < n]}}{(D:\partialcubset{l}{n})~(d:\mybox{l}{n,p}(D))}{:}{\myfullbox{l}{n-1}(\hd(D))}

  \eqnline{\downbox{l,\epsilon,q}{n,q+1}}{D~(d,b)}{\defeq}{\border{l}^{n-1,q}(\hd(D))(\downbox{l,\epsilon,q}{n,q}(D)(d))(b_{\epsilon})}

  \eqnline{\downbox{l,\epsilon,q}{n,p,[q < p-1]}}{D~(d,b)}{\defeq}{\downbox{l,\epsilon,q}{n,p-1}(D)(d)}
\end{eqntable}
